General purpose gene annotation using deep learning

### 2020-03-27 paper/main.tex
minor

\begin{table}[!t]
\processtable{Experimental Results and Comparison\label{Tab:03}} {
\begin{tabular}{@{}lll@{}}
\toprule & EnsemblMetazoa & JGI Phytosome\\
\midrule
Augustus & 0.62 (+-0.02) & 0.83 (+- 0.03)\\
Dilated CNN Baseline & 0.62 (+-0.02) & 0.83 (+- 0.03)\\
Best Helixer model & 0.62 (+-0.02) & 0.72 (+-0.02) \\
Best model + varied input length & 0.62 (+-0.02) & 0.72 (+-0.02) \\
Best model + varied input length + overlapping & 0.62 (+-0.02) & 0.72 (+-0.02) \\
Varied input length + overlapping + ensembling & 0.62 (+-0.02) & 0.72 (+-0.02) \\
\botrule
\end{tabular}}{Values are averages in CDS F1 (?) across all validation and test genomes of the \\ respective group.}
\end{table}

>>>>

\begin{table}[!t]
\processtable{Experimental Results and Comparison\label{Tab:03}} {
\begin{tabular}{@{}lll@{}}
\toprule & Animals & Plants\\
\midrule
Augustus & 0.632 (+-0.089) & - (+-)\\
Dilated CNN Baseline & - (+-) & - (+-)\\
Best Helixer model & - (+-) & - (+-) \\
Best model + varied input length & - (+-) & - (+-) \\
Best model + varied input length + overlapping & - (+-) & - (+-) \\
Varied input length + overlapping + ensembling & - (+-) & - (+-) \\
\botrule
\end{tabular}}{Values are the median in Subgenic F1 across all validation and test genomes of the respective group.}
\end{table}
